251 MA

### 2022-12-13 code/process.Rmd
more coding of betas

# TODOs
- why are some ES's  about 2 times bigger than they should be? (from within v between stuff)
- validate df against num people?
 - what to do for chisq, other things? for ES

@@

  select(target_lastauthor_year, status, academic_year, subfield, target_year, stanford_internal, 
         open_data, open_materials, target_on_turk, replication_on_turk, 
         within_between, single_vignette, repeated_measure,
         target_N, target_test, target_raw_stat, target_pvalue, target_ES_type, target_ES_value,
         same_dir,
         replication_N, replication_test, replication_raw_stat, replication_pvalue, replication_ES_type, replication_ES_value,
         replicated_instructor_code, replicated_report_code)

@@

d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> tally()
```
We have maybe as many as 178 at least for some analyses.

@@

```{r}
d_val <- d |> filter(!status %in% c("missing", "non-experiment", "reproduction", "TODO"))

@@

parse_beta_se <- function(raw_stat){
    beta=str_extract(raw_stat, "b=.*\\(") |> str_sub(3,-2) |> as.numeric()
    se=str_extract(raw_stat, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
    zval=beta/se
    print(zval)
    pval=2*pnorm(zval, lower.tail=F)
return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=NA, "N_calc"=NA, "beta"=beta, "SE"=se))
}

@@

do_blanks <- function(){
  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "beta"=NA, "SE"=NA))
}
do_parsing=function(raw_stat, within_between,n){
  if (is.na(raw_stat)) {return (do_blanks())}
  if (str_sub(raw_stat,1,1)=="t"){return(parse_t(raw_stat, within_between))}
  if (str_sub(raw_stat,1,1)=="F"){return(parse_f(raw_stat, within_between))}
  if (str_sub(raw_stat,1,1)=="c"){return(parse_chisq(raw_stat, within_between))}
  if (str_sub(raw_stat, 1,3)=="MCI"){return(parse_mean_ci(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,3)=="MSD"){return(parse_mean_sd(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,3)=="MSE"){return(parse_mean_se(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,8)=="wilcoxon"){return(parse_wilcoxon(raw_stat))}
  if (str_sub(raw_stat, 1,3)=="bse"){return(parse_beta_se(raw_stat))}

@@

@@

test |> filter(is.na(target_d_calc)) |> filter(!is.na(target_raw_stat)) |>  pull(target_raw_stat)

test |> filter(is.na(rep_d_calc)) |> filter(!is.na(replication_raw_stat)) |> pull(replication_raw_stat)
```

@@

d_es_try <- d_es |> filter(!is.na(target_d_calc)&!is.na(rep_d_calc)|!is.na(target_beta)&!is.na(rep_beta)) |> 
  mutate(
         predInt=ifelse(!is.na(target_d_calc),
                        Replicate::pred_int(target_d_calc,target_se_calc**2, rep_d_calc, rep_se_calc**2)$rep.inside,
                        Replicate::pred_int(target_beta, target_SE**2, rep_beta, rep_SE**2)$rep.inside),
         p_orig=ifelse(!is.na(target_d_calc),
                       Replicate::p_orig(target_d_calc,target_se_calc**2, rep_d_calc, t2=0, rep_se_calc**2),
                       Replicate::p_orig(target_beta, target_SE**2,rep_beta, t2=0, rep_SE**2)))

@@

d_es_try |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=p_orig))+
  geom_point()+
  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=F, direction=-1)+
  labs(color="p_orig", x="Original SMD", y="Replication SMD")

d_es_try |> mutate(p_sig=p_orig<.05) |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=p_sig))+
  geom_point()+
  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=T, direction=-1)+
  labs(color="P_orig<.05", x="Original SMD", y="Replication SMD")

d_es_try |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=predInt))+
  geom_point()+
  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=T, direction=-1)+
  labs(color="rep in predInt", x="Original SMD", y="Replication SMD")

d_es_try |> ggplot(aes(x=replicated_report_code, y=p_orig))+geom_jitter(height=0, alpha=.5)+
  #scale_y_log10()+
  geom_hline(yintercept=.05)

d_es_try |> ggplot(aes(x=replicated_report_code, y=predInt))+geom_jitter(alpha=.5)
```

@@

```{r, message=T}
message("total rows")
d_es |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> nrow()

@@

d_check_nas <- d_es |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> ungroup() |>
    select(-rep_fstat, -rep_tstat,-rep_df_1,-rep_df_2,
         -target_fstat, -target_tstat, -target_df_1, -target_df_2,
         -d_fill_rep, -d_fill_target, 
         -replication_ES_type, -replication_ES_value, -replication_pvalue,
         -target_ES_type, -target_ES_value, -target_pvalue,
         -rep_N_calc, -target_N_calc,
         -replication_test, -target_test)

d_check_nas |> summarize(                                                      across(everything(),~sum(is.na(.)))) |>
pivot_longer(everything()) |>
  arrange(desc(value)) |>
  filter(value!=0)

message("number of complete rows")

@@

@@

# Correlation between replication scores

```{r, message=T}
d_corr <- d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |>
  mutate(replicated_instructor_code=as.numeric(replicated_instructor_code)) |> #forcibly convert the ?s to NAs
  filter(!is.na(replicated_instructor_code) & !is.na(replicated_report_code))

corr <- cor.test(d_corr$replicated_instructor_code, d_corr$replicated_report_code, method = 'spearman')

message("Num not match")
d_corr |> filter(replicated_instructor_code!=replicated_report_code) |> nrow()

message("Num match")
d_corr |> filter(replicated_instructor_code==replicated_report_code) |> nrow()

message("distribution of non-matches")

ggplot(d_corr |> filter(replicated_instructor_code!=replicated_report_code), aes(x=replicated_instructor_code, y=replicated_report_code))+geom_jitter(width=.04, height=.04)+theme_bw()

d_corr |>
  group_by(replicated_instructor_code, replicated_report_code ) |> tally() |> arrange(replicated_report_code) |>
  pivot_wider(names_from=replicated_report_code, values_from=n, values_fill=0)
```

NOTE: will need to replace replicated_code with the discussion agreed one!!

## demographics

```{r}
d_demo <- d_es |> 
  ungroup() |> 
  mutate(pub_year= target_year-mean(target_year)) |> 
  select(target_year, pub_year, subfield, replicated_report_code, academic_year)

summary(d_demo)
d_demo |> group_by(subfield) |> tally()
```

## statistics

? will outliers on ratio_ss cause a problem?

```{r}
d_stats <- d_es |> 
  mutate(log_p =log(target_p_calc),
         log_sample =log(target_N),
         ratio_ss = replication_N/target_N,
         change_platform=ifelse(replication_on_turk==target_on_turk,0,1)) |> 
  #this codes 1 if the original was in person, but replication turk/prolific,
  # 0 if they were both on turk/prolific or both in-person (rare, but happens a few times)
  select(replicated_report_code,log_p,log_sample, ratio_ss, change_platform, academic_year, target_d_calc)

summary(d_stats)
```

## closeness

# could do with mutate across, but clearer this way?

d_close <- d_es |> 
  mutate(open_data=ifelse(open_data=="yes", 1,0),
         open_mat=ifelse(open_materials=="yes", 1,0),
         stanford=ifelse(stanford_internal=="yes", 1,0)) |> 
  select(open_data, open_mat, stanford, replicated_report_code,
         academic_year)

summary(d_close)
```

## design

```{r}
d_design <- d_es |> 
  mutate(is_within=case_when(
    within_between=="within" ~ 1,
    within_between=="mixed" ~ 1,
    within_between=="between" ~ 0),
    log_trials=log(repeated_measure),
    log_sample=log(target_N))|> 
  select(is_within, single_vignette,log_trials, log_sample, replicated_report_code, academic_year)

summary(d_design)
```

>>>>

@@

  select(target_lastauthor_year, status, academic_year, subfield, target_year, stanford_internal, 
         open_data, open_materials, target_on_turk, replication_on_turk, 
         within_between, single_vignette, repeated_measure,
         target_N, target_test, target_raw_stat, target_pvalue, target_ES_type, target_ES_value,
         same_dir,
         replication_N, replication_test, replication_raw_stat, replication_pvalue, replication_ES_type, replication_ES_value,
         replicated_instructor_code, replicated_report_code, adjudicated_replication_code)

@@

d |> filter(!status %in% c("missing", "non-experiment", "reproduction", "TODO")) |> tally()
```
We have maybe as many as 178 at least for some analyses.

@@

```{r}
d_val <- d |> filter(!status %in% c("missing", "non-experiment", "reproduction"))

@@

parse_beta_se <- function(raw_stat){
    beta=str_extract(raw_stat, "b=.*\\(") |> str_sub(3,-2) |> as.numeric()
    se=str_extract(raw_stat, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
    zval=beta/se
    pval=2*pnorm(zval, lower.tail=F)
return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=NA, "N_calc"=NA, "beta"=beta, "SE"=se))
}

```{r}
parse_beta_ci <- function(raw_stat){
  beta=str_extract(raw_stat, "b=.*\\[") |> str_sub(3,-2) |> as.numeric()
  low=str_extract(raw_stat, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
  high=str_extract(raw_stat, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  se=high-low/(2*1.96)
  zval=beta/se
    pval=2*pnorm(zval, lower.tail=F)
  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=NA, "N_calc"=NA, "beta"=beta, "SE"=se))
}

@@

do_blanks <- function(){
  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "beta"=NA, "SE"=NA))
}
do_parsing=function(raw_stat, within_between,n){
  if (is.na(raw_stat)) {return (do_blanks())}
  if (str_sub(raw_stat,1,1)=="t"){return(parse_t(raw_stat, within_between))}
  if (str_sub(raw_stat,1,1)=="F"){return(parse_f(raw_stat, within_between))}
  if (str_sub(raw_stat,1,1)=="c"){return(parse_chisq(raw_stat, within_between))}
  if (str_sub(raw_stat, 1,3)=="MCI"){return(parse_mean_ci(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,3)=="MSD"){return(parse_mean_sd(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,3)=="MSE"){return(parse_mean_se(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,8)=="wilcoxon"){return(parse_wilcoxon(raw_stat))}
  if (str_sub(raw_stat, 1,3)=="bse"){return(parse_beta_se(raw_stat))}
  if (str_sub(raw_stat, 1,3)=="bci"){return(parse_beta_se(raw_stat))}

@@

note that we also aren't including the betas where we know we can't get effect size, but we'll still get porig and predInt.

@@

test |> filter(is.na(target_d_calc)&is.na(target_beta)) |> filter(!is.na(target_raw_stat)) |>  pull(target_raw_stat)

test |> filter(is.na(rep_d_calc)&is.na(rep_beta)) |> filter(!is.na(replication_raw_stat)) |> pull(replication_raw_stat)
```

@@

```{r}
do_pred_int <- function(target_d_calc, target_se_calc, rep_d_calc,rep_se_calc, target_beta, target_SE, rep_beta, rep_SE){
  if (!is.na(target_d_calc)&!is.na(rep_d_calc)){
    return(Replicate::pred_int(target_d_calc,target_se_calc**2, rep_d_calc, rep_se_calc**2)$rep.inside)}
  if(!is.na(target_beta)&!is.na(rep_beta)){
    return(Replicate::pred_int(target_beta, target_SE**2, rep_beta, rep_SE**2)$rep.inside)
  }
  return(NA)
}

do_p_orig <- function(target_d_calc, target_se_calc, rep_d_calc,rep_se_calc, target_beta, target_SE, rep_beta, rep_SE){
  if (!is.na(target_d_calc)&!is.na(rep_d_calc)){
    return(Replicate::p_orig(target_d_calc,target_se_calc**2, rep_d_calc, t2=0, rep_se_calc**2))}
  if(!is.na(target_beta)&!is.na(rep_beta)){
    return(Replicate::p_orig(target_beta, target_SE**2,rep_beta, t2=0, rep_SE**2))
  }
  return(NA)
}

do_subjective_rep <- function(replicated_instructor_code, replicated_report_code, adjudicated_replication_code){
  if (is.na(replicated_instructor_code)){return(as.numeric(NA))}
  if (is.na(replicated_report_code)){return(as.numeric(NA))}
  if (replicated_instructor_code==replicated_report_code){ return(replicated_instructor_code)}
  if (!is.na(adjudicated_replication_code)){return (adjudicated_replication_code)}
  return(as.numeric(NA))
}
d_es_predInt <- d_es |> 
         mutate(
           predInt=do_pred_int(target_d_calc, target_se_calc, rep_d_calc,rep_se_calc, target_beta, target_SE, rep_beta, rep_SE),
           p_orig=do_p_orig(target_d_calc, target_se_calc, rep_d_calc,rep_se_calc, target_beta, target_SE, rep_beta, rep_SE),
           sub_rep= do_subjective_rep(replicated_instructor_code, replicated_report_code, adjudicated_replication_code))

@@

d_es_predInt |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=p_orig))+
  geom_point()+
  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=F, direction=-1)+
  labs(color="p_orig", x="Original SMD", y="Replication SMD")

d_es_predInt |> mutate(p_sig=p_orig<.05) |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=p_sig))+
  geom_point()+
  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=T, direction=-1)+
  labs(color="P_orig<.05", x="Original SMD", y="Replication SMD")

d_es_predInt |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=predInt))+
  geom_point()+
  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=T, direction=-1)+
  labs(color="rep in predInt", x="Original SMD", y="Replication SMD")

# d_es_predInt |> ggplot(aes(x=replicated_report_code, y=p_orig))+geom_jitter(height=0, alpha=.5)+
#   #scale_y_log10()+
#   geom_hline(yintercept=.05)
# 
# d_es_predInt |> ggplot(aes(x=replicated_report_code, y=predInt))+geom_jitter(alpha=.5)
```

@@

```{r, message=T}
message("total rows")
d_es_predInt |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> nrow()

@@

d_check_nas <- d_es_predInt |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> ungroup() |>
    select(target_lastauthor_year, status, academic_year, subfield, target_year,
           stanford_internal,open_data, open_materials, target_on_turk,
           replication_on_turk, within_between, single_vignette, repeated_measure,
           target_N, replication_N,
           target_p_calc, target_d_calc, rep_p_calc, rep_d_calc,
           predInt, p_orig, sub_rep)

d_check_nas |> summarize(across(everything(),~sum(is.na(.)))) |>
pivot_longer(everything()) |>
  arrange((value)) |>
  filter(value!=0)

message("number of complete rows for full analysis")

@@

message("number of rows for subjective w/ demographic/experimental")

d_check_nas |> select(target_lastauthor_year, status, academic_year, subfield, target_year,
           stanford_internal,open_data, open_materials, target_on_turk,
           replication_on_turk, within_between, single_vignette, repeated_measure,
           target_N, replication_N,
           sub_rep) |> filter(across(everything(), ~!is.na(.))) |> nrow()

message("number of rows for predInt/p_orig w/ demographic/experimental")

d_check_nas |> select(target_lastauthor_year, status, academic_year, subfield, target_year,
           stanford_internal,open_data, open_materials, target_on_turk,
           replication_on_turk, within_between, single_vignette, repeated_measure,
           target_N, replication_N, predInt, p_orig,
           sub_rep) |>  filter(across(everything(), ~!is.na(.))) |> nrow()
```

```{r}
d_for_model <- d_es_predInt |> 
  ungroup() |> 
  mutate(pub_year= target_year-mean(target_year),
         log_p =log(target_p_calc),
         log_sample =log(target_N),
         ratio_ss = replication_N/target_N,
         change_platform=ifelse(replication_on_turk==target_on_turk,0,1),
  #this codes 1 if the original was in person, but replication turk/prolific,
  # 0 if they were both on turk/prolific or both in-person (rare, but happens a few times)
        open_data=ifelse(open_data=="yes", 1,0),
         open_mat=ifelse(open_materials=="yes", 1,0),
         stanford=ifelse(stanford_internal=="yes", 1,0),
        is_within=case_when(
            within_between=="within" ~ 1,
            within_between=="mixed" ~ 1,
            within_between=="between" ~ 0),
    log_trials=log(repeated_measure)) |> 
  select(target_lastauthor_year, academic_year, subfield, 
         pub_year, log_p, log_sample, ratio_ss, change_platform, target_d_calc,
           stanford, open_data, open_mat, 
         is_within, single_vignette, log_trials, 
           predInt, p_orig, sub_rep)

summary(d_for_model)

@@
